---
title: "MPNST project"
subtitle: "All patients datasets"
author: "Audrey"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document:
    code_folding: show
    code_download: true
    toc: true
    toc_float: true
    number_sections: false
---

<style>
body {
text-align: justify}
</style>

```{r clean, echo = FALSE}
rm(list = ls())
```

<!-- Automatically computes and prints in the output the running time for any code chunk -->
```{r, echo=FALSE}
# https://github.com/rstudio/rmarkdown/issues/1453
hooks = knitr::knit_hooks$get()
hook_foldable = function(type) {
  force(type)
  function(x, options) {
    res = hooks[[type]](x, options)
    
    if (isFALSE(options[[paste0("fold_", type)]])) return(res)
    
    paste0(
      "<details><summary>", "show", "</summary>\n\n",
      res,
      "\n\n</details>"
    )
  }
}
knitr::knit_hooks$set(
  output = hook_foldable("output"),
  plot = hook_foldable("plot"),
  time_it = local({
    now = NULL
    function(before, options) {
      if (options$time_it) {
        if (before) {
          now <= as.numeric(Sys.time())
        } else {
          res = as.numeric(Sys.time()) - now # seconds
          paste("(Time to run :", round(res, digits = 2), "s)")
        }
      }
    }
  })
)
```

<!-- Set default parameters for all chunks -->
```{r, setup, include = FALSE}
set.seed(1337L)
knitr::opts_chunk$set(echo = TRUE, # display code
                      # display chunk output
                      message = FALSE,
                      warning = FALSE,
                      fold_output = FALSE, # usefull for sessionInfo()
                      fold_plot = FALSE,
                      
                      # figure settings
                      fig.align = 'center',
                      fig.width = 20,
                      fig.height = 15,
                      
                      # something about seed, chunk and Rmarkdown compilation
                      # https://stackoverflow.com/questions/39417003/long-vectors-not-supported-yet-error-in-rmd-but-not-in-r-script
                      # cache = TRUE,
                      cache.lazy = FALSE, 
                      
                      # add runtime after chunk
                      time_it = FALSE)
```


This file is used to make a tumor cells dataset, to then run trajectory inference tools.

```{r library}
library(dplyr)
library(patchwork)
library(ggplot2)
library(ComplexHeatmap)
```


# Preparation

In this section, we set the global settings of the analysis. We will store data there :

```{r out_dir}
save_name = "tumor_patients"
out_dir = "/home/aurelien/Documents/Audrey/git_analysis/mpnst_project/6_tumor_cells_patients/"
```

We load the sample information :

```{r custom_palette_sample, fig.width = 10, fig.height = 1}
sample_info = readRDS(file = paste0(out_dir, "/../4_combined_patients/all_patients_sample_info.rds"))

project_names_oi = as.character(sample_info$project_name)

ggplot2::ggplot(sample_info) +
  ggplot2::geom_label(aes(x = project_name, y = 0, label = project_name, fill = project_name)) +
  ggplot2::geom_text(aes(x = project_name, y = 1, label = sample_identifier)) +
  ggplot2::lims(y = c(-1, 2)) +
  ggplot2::scale_fill_manual(values = sample_info$color, breaks = sample_info$project_name) +
  ggplot2::theme_void() +
  ggplot2::theme(legend.position = "none")
```

Here are custom colors for each cell type :

```{r color_markers, fig.width = 10, fig.height = 1, class.source = "fold-hide"}
color_markers = readRDS(paste0(out_dir, "/../1_metadata/datasets_color_markers.rds"))

data.frame(cell_type = names(color_markers),
           color = unlist(color_markers)) %>%
  ggplot2::ggplot(., aes(x = cell_type, y = 0, fill = cell_type)) +
  ggplot2::geom_point(pch = 21, size = 5) +
  ggplot2::scale_fill_manual(values = unlist(color_markers), breaks = names(color_markers)) +
  ggplot2::theme_classic() +
  ggplot2::theme(legend.position = "none",
                 axis.line = element_blank(),
                 axis.title = element_blank(),
                 axis.ticks = element_blank(),
                 axis.text.y = element_blank())
```

# Make `r save_name` dataset

## Individual datasets

We extract a cluster annotated as `r save_name` in each dataset. For each sample, we :

* load individual dataset
* look at `r save_name` markers
* look at `r save_name` score for each cluster
* select the best clusters based on average `r save_name` score

We load individual datasets :

```{r sobj_list}
sobj_list = lapply(project_names_oi, FUN = function(one_project_name) {
  subsobj = readRDS(paste0(out_dir, "/../3_individual_patients/filtered/",
                           one_project_name, "_sobj_filtered.rds"))
  return(subsobj)
})
names(sobj_list) = project_names_oi

lapply(sobj_list, FUN = dim) %>%
  do.call(rbind, .)
```


We represent cells in the tSNE :

```{r name2D}
name2D = "RNA_pca_20_tsne"
```


We look gene markers expression level on the projection, to locate immune cells :

```{r gene_expression, fig.width = 12, fig.height = 80}
tumor_markers = c("DLK1", "SOX10", "PLP1")

plot_list = lapply(sobj_list, FUN = function(one_sobj) {
  subtitle = as.character(unique(one_sobj$project_name))
  plot_sublist = lapply(tumor_markers, FUN = function(one_gene) {
    p = Seurat::FeaturePlot(one_sobj, reduction = name2D,
                            features = one_gene) +
      ggplot2::labs(subtitle = subtitle) +
      Seurat::NoAxes() +
      ggplot2::scale_color_gradientn(colors = aquarius:::color_gene) +
      ggplot2::theme(aspect.ratio = 1,
                     plot.subtitle = element_text(hjust = 0.5))
    return(p)
  })
  return(plot_sublist)
}) %>% unlist(., recursive = FALSE)

patchwork::wrap_plots(plot_list, ncol = length(tumor_markers))
```

We attribute a score for immune cells in each dataset :

```{r score_immune_cells}
tumor_markers = c("SOX10", "SOX9", "PLP1", "DLK1", "PDGFRA", "PDGFA",
                  "PDGFRB", "PDGFB", "POSTN", "GPM6B", "GAS1",
                  "CXCL12", "PRSS23", "CRABP1", "SFRP1", "SERPINE2", "CCNB1IP1",
                  toupper(aquarius::cell_markers$`tumor cells`)) %>% unique()

sobj_list = lapply(sobj_list, FUN = function(one_sobj) {
  one_sobj$tumor_score = Seurat::AddModuleScore(
    one_sobj,
    features = list(tumor_markers))$Cluster1
  
  return(one_sobj)
})
```

We identify a threshold to select cells :

```{r score_vector, fig.width = 10, fig.height = 5}
score_vector = lapply(sobj_list, FUN = function(one_sobj) {
  return(one_sobj$tumor_score)
}) %>% unlist() %>% unname()

hist(score_vector, breaks = 200,
     xlab = "Score for tumor cells",
     ylab = "Number of cells",
     main = "Histogram")
```


We add a new column to then select cells.

```{r add_is_oi}
mean_score_thresh = 0.1

sobj_list = lapply(sobj_list, FUN = function(one_sobj) {
  ## Score by cluster
  score_by_clusters = one_sobj@meta.data %>%
    dplyr::select(seurat_clusters, tumor_score) %>%
    dplyr::group_by(seurat_clusters) %>%
    dplyr::summarise(avg_score = mean(tumor_score)) %>%
    as.data.frame()
  
  ## Cluster of interest
  cluster_of_interest = score_by_clusters %>%
    dplyr::filter(avg_score > mean_score_thresh) %>%
    dplyr::pull(seurat_clusters) %>%
    as.character()
  one_sobj$is_of_interest = ifelse(one_sobj$seurat_clusters %in% cluster_of_interest,
                                   yes = TRUE, no = FALSE)
  
  ## Output
  return(one_sobj)
})

lapply(sobj_list, FUN = function(one_sobj) {
  table(one_sobj$is_of_interest)
}) %>% do.call(rbind, .) %>%
  rbind(., colSums(.))
```


We represent, on the projection, score, clusters we will select, and represent the average score for each cluster, by dataset.

```{r score_by_clusters, fig.width = 12, fig.height = 80, class.source = "fold-hide"}
plot_list = lapply(sobj_list, FUN = function(one_sobj) {
  project_name = as.character(unique(one_sobj$project_name))
  
  #--------------------- copied-pasted
  ## Score by cluster
  score_by_clusters = one_sobj@meta.data %>%
    dplyr::select(seurat_clusters, tumor_score) %>%
    dplyr::group_by(seurat_clusters) %>%
    dplyr::summarise(avg_score = mean(tumor_score)) %>%
    as.data.frame()
  
  ## Cluster of interest
  cluster_of_interest = score_by_clusters %>%
    dplyr::filter(avg_score > mean_score_thresh) %>%
    dplyr::pull(seurat_clusters) %>%
    as.character()
  #---------------------
  
  ## Number of cells
  nb_cells_ind = sum(one_sobj$tumor_score > mean_score_thresh)
  nb_cells_clust = sum(one_sobj$seurat_clusters %in% cluster_of_interest)
  
  ## Figure
  p_score = Seurat::FeaturePlot(one_sobj, reduction = name2D,
                                features = "tumor_score") +
    ggplot2::labs(title = paste0(nb_cells_ind, " cells"),
                  subtitle = paste0("Score for tumor cells"),
                  y = project_name) +
    ggplot2::scale_color_gradient2(low = aquarius:::color_cnv[1],
                                   mid = aquarius:::color_cnv[2],
                                   high = aquarius:::color_cnv[3],
                                   midpoint = 0) +
    Seurat::NoAxes() +
    ggplot2::theme(aspect.ratio = 1,
                   plot.subtitle = element_text(hjust = 0.5),
                   axis.title.y = element_text(size = 20, face = "bold", angle = 90))
  
  p_cluster = Seurat::DimPlot(one_sobj, reduction = name2D,
                              group.by = "is_of_interest") +
    ggplot2::labs(title = paste0(nb_cells_clust, " cells"),
                  subtitle = paste0("Clusters : ", paste(cluster_of_interest, collapse = ", "))) +
    Seurat::NoAxes() + Seurat::NoLegend() +
    ggplot2::theme(aspect.ratio = 1,
                   plot.title = element_text(hjust = 0.5),
                   plot.subtitle = element_text(hjust = 0.5))
  
  p_mean = ggplot2::ggplot(score_by_clusters, aes(x = seurat_clusters, y = avg_score)) +
    ggplot2::geom_point() +
    ggplot2::geom_hline(yintercept = mean_score_thresh, col = "red") +
    ggplot2::labs(x = "Cluster ID", y = "Mean score",
                  title = "Mean score by cluster") +
    ggplot2::theme_classic() +
    ggplot2::theme(plot.title = element_text(hjust = 0.5, face = "bold"))
  
  ## Output
  return(list(p_score, p_cluster, p_mean))
}) %>% unlist(., recursive = FALSE)

patchwork::wrap_plots(plot_list, ncol = 3, widths = c(1,1,2))
```


## Combined dataset

For each sample, we extract cells of interest based on clusters mean score, and build a new dataset.

```{r subset_is_of_interest}
sobj_list = lapply(sobj_list, FUN = function(one_sobj) {
  if (sum(one_sobj$is_of_interest) > 0) {
    one_sobj = subset(one_sobj, is_of_interest == TRUE)
  } else {
    one_sobj = NA
  }
  return(one_sobj)
})

lapply(sobj_list, FUN = dim) %>%
  do.call(rbind, .) %>%
  rbind(., colSums(.))
```


We combine all datasets :

```{r merge_datasets}
sobj = base::merge(sobj_list[[1]],
                   y = sobj_list[c(2:length(sobj_list))],
                   add.cell.ids = project_names_oi)

rm(sobj_list)
sobj
```


We set factor levels in the Seurat object :

```{r sobj_set_factor_levels}
sobj$orig.ident = factor(sobj$orig.ident,
                         levels = levels(sample_info$project_name))
sobj$project_name = factor(sobj$project_name,
                           levels = levels(sample_info$project_name))
sobj$sample_identifier = factor(sobj$sample_identifier,
                                levels = levels(sample_info$sample_identifier))
sobj$genotype = factor(sobj$genotype,
                       levels = levels(sample_info$genotype))
sobj$sample_type = factor(sobj$sample_type,
                          levels = levels(sample_info$sample_type))
sobj$cell_type = factor(sobj$cell_type,
                        levels = names(color_markers))
```

# Processing

We remove genes that are expressed in less than 5 cells :

```{r filter_genes}
sobj = aquarius::filter_features(sobj, min_cells = 5)
sobj
```

## Metadata

How many cells by sample ?

```{r table_orig_ident}
table(sobj$project_name)
```

We represent this information as a barplot :

```{r barplot_count, fig.width = 4, fig.height = 5}
aquarius::plot_barplot(df = table(sobj$project_name) %>%
                         as.data.frame.table() %>%
                         dplyr::mutate(x = "Cells"),
                       x = "x", y = "Freq", fill = "Var1",
                       position = position_fill()) +
  ggplot2::scale_fill_manual(values = sample_info$color,
                             breaks = sample_info$project_name,
                             name = "Sample of origin")
```


## Projection

We normalize the count matrix for remaining cells :

```{r normalization}
sobj = Seurat::NormalizeData(sobj,
                             normalization.method = "LogNormalize")
sobj = Seurat::FindVariableFeatures(sobj, nfeatures = 2000)
sobj = Seurat::ScaleData(sobj)

sobj
```

We remove batch-effect using FastMNN :

```{r fastmnn}
sobj_mnn = Seurat::SplitObject(sobj, split.by = "project_name")
sobj_mnn = aquarius::integration_fastmnn(object.list = sobj_mnn,
                                         assay = "RNA",
                                         verbose = TRUE)

sobj@assays[["mnn.reconstructed"]] = sobj_mnn@assays[["mnn.reconstructed"]]
sobj@reductions[["mnn"]] = sobj_mnn@reductions[["mnn"]]

rm(sobj_mnn)

sobj
```

We generate a diffusion map :

```{r diffusion_map, time_it = TRUE}
sobj = aquarius::run_diffusion_map(sobj = sobj,
                                   input = "mnn",
                                   seed = 1337L,
                                   verbose = TRUE,
                                   n_eigs = 50,
                                   suppress_dpt = TRUE,
                                   return_dm = FALSE)
```

We visualize the diffusion map :

```{r see_dm, fig.width = 8, fig.height = 7}
Seurat::DimPlot(sobj, group.by = "project_name",
                reduction = "mnn_dm", dims = c(1,6)) +
  ggplot2::scale_color_manual(values = sample_info$color,
                              breaks = sample_info$project_name) +
  Seurat::NoAxes() + ggplot2::ggtitle("RNA - mnn - DM") +
  ggplot2::theme(aspect.ratio = 1,
                 plot.title = element_text(hjust = 0.5)) +
  ggplot2::guides(color = guide_legend(override.aes = list(size = 3), ncol = 1))
```


We generate a UMAP from the diffusion map :

```{r mnn_dm_umap}
ndims = 49
sobj = Seurat::RunUMAP(sobj,
                       reduction = "mnn_dm",
                       dims = 1:ndims,
                       seed.use = 1337L,
                       reduction.name = paste0("mnn_dm_", ndims, "_umap"))
```

## Visualization

We visualize this representation :

```{r see_umap_tsne, fig.width = 8, fig.height = 7}
Seurat::DimPlot(sobj, group.by = "project_name",
                reduction = paste0("mnn_dm_", ndims, "_umap")) +
  ggplot2::scale_color_manual(values = sample_info$color,
                              breaks = sample_info$project_name) +
  Seurat::NoAxes() + ggplot2::ggtitle("RNA - mnn - DM - UMAP") +
  ggplot2::theme(aspect.ratio = 1,
                 plot.title = element_text(hjust = 0.5)) +
  ggplot2::guides(color = guide_legend(override.aes = list(size = 3), ncol = 1))
```

There is a competition between fibroblasts and tumor cells annotation. Maybe we mis-selected cells, and there are fibroblasts in this representation. We visualize the annotation :

```{r see_dm_umap_celltype, fig.width = 8, fig.height = 7}
Seurat::DimPlot(sobj, group.by = "cell_type",
                reduction = paste0("mnn_dm_", ndims, "_umap"),
                cols = color_markers) +
  Seurat::NoAxes() + ggplot2::ggtitle("RNA - mnn - DM - UMAP") +
  ggplot2::theme(aspect.ratio = 1,
                 plot.title = element_text(hjust = 0.5)) +
  ggplot2::guides(color = guide_legend(override.aes = list(size = 3), ncol = 1))
```

We make a representation split by origin :

```{r plot_split2, fig.width = 12, fig.height = 17}
plot_list = aquarius::plot_split_dimred(sobj,
                                        reduction = paste0("mnn_dm_", ndims, "_umap"),
                                        split_by = "project_name",
                                        split_color = sample_info$color,
                                        group_by = "cell_type",
                                        group_color = color_markers)

patchwork::wrap_plots(plot_list, ncol = 4) +
  patchwork::plot_layout(guides = "collect") &
  guides(color = guide_legend(override.aes = list(size = 4), title = "Cell type"))
```


# Re-extraction

## Clustering

We make a clustering on the diffusion map :

```{r clustering_mnn_dm, fig.width = 8, fig.height = 7}
sobj = Seurat::FindNeighbors(sobj, reduction = "mnn_dm", dims = c(1:ndims))
sobj = Seurat::FindClusters(sobj, resolution = 1)

Seurat::DimPlot(sobj, reduction = paste0("mnn_dm_", ndims, "_umap"),
                group.by = "seurat_clusters", label = TRUE) +
  Seurat::NoAxes() + Seurat::NoLegend() +
  ggplot2::labs(title = "Cluster ID") +
  ggplot2::theme(aspect.ratio = 1,
                 plot.title = element_text(hjust = 0.5))
```

We manually subset cells based on clustering :

```{r extract_clusters, fig.width = 8, fig.height = 7}
sobj$choosen = sobj$seurat_clusters %in% c(46,23,16,35,32,29,37,8,3,42,
                                           17,25,47,34,31,40,39,51,20,
                                           45,7,49,21,15,18,2,36,38,12,
                                           13,6,50,1,11)

Seurat::DimPlot(sobj, reduction = paste0("mnn_dm_", ndims, "_umap"), group.by = "choosen") +
  Seurat::NoAxes() +
  ggplot2::labs(title = "Choosen clusters (tumor cells ?)") +
  ggplot2::theme(aspect.ratio = 1,
                 plot.title = element_text(hjust = 0.5))
```

## Selection

We keep only cells of interest :

```{r re_subset}
sobj = subset(sobj, choosen)
sobj
```

We remove all projections :

```{r remove_reductions}
sobj@reductions[names(sobj@reductions)] = NULL
sobj
```

How many cells by sample ?

```{r table_orig_ident2}
table(sobj$project_name)
```

## Processing

We remove genes that are expressed in less than 5 cells :

```{r filter_genes2}
sobj = aquarius::filter_features(sobj, min_cells = 5)
sobj
```


We normalize the count matrix for remaining cells :

```{r normalization2}
sobj = Seurat::NormalizeData(sobj,
                             normalization.method = "LogNormalize")
sobj = Seurat::FindVariableFeatures(sobj, nfeatures = 2000)
sobj = Seurat::ScaleData(sobj)

sobj
```

We remove batch-effect using FastMNN :

```{r fastmnn2}
sobj_mnn = Seurat::SplitObject(sobj, split.by = "project_name")
sobj_mnn = aquarius::integration_fastmnn(object.list = sobj_mnn,
                                         assay = "RNA",
                                         verbose = TRUE)

sobj@assays[["mnn.reconstructed"]] = sobj_mnn@assays[["mnn.reconstructed"]]
sobj@reductions[["mnn"]] = sobj_mnn@reductions[["mnn"]]

rm(sobj_mnn)

sobj
```

We generate a diffusion map :

```{r diffusion_map2, time_it = TRUE}
sobj = aquarius::run_diffusion_map(sobj = sobj,
                                   input = "mnn",
                                   seed = 1337L,
                                   verbose = TRUE,
                                   n_eigs = 50,
                                   suppress_dpt = TRUE,
                                   return_dm = FALSE)
```

We visualize the diffusion map :

```{r see_dm2, fig.width = 8, fig.height = 7}
Seurat::DimPlot(sobj, group.by = "project_name",
                reduction = "mnn_dm", dims = c(1,5)) +
  ggplot2::scale_color_manual(values = sample_info$color,
                              breaks = sample_info$project_name) +
  Seurat::NoAxes() + ggplot2::ggtitle("RNA - mnn - DM") +
  ggplot2::theme(aspect.ratio = 1,
                 plot.title = element_text(hjust = 0.5)) +
  ggplot2::guides(color = guide_legend(override.aes = list(size = 3), ncol = 1))
```


We generate a UMAP from the diffusion map :

```{r mnn_dm_umap2}
ndims = 8
sobj = Seurat::RunUMAP(sobj,
                       reduction = "mnn_dm",
                       dims = 1:ndims,
                       seed.use = 1337L,
                       reduction.name = paste0("mnn_dm_", ndims, "_umap"))
```

## Visualization

We visualize this representation :

```{r see_umap_tsne2, fig.width = 8, fig.height = 7}
Seurat::DimPlot(sobj, group.by = "project_name",
                reduction = paste0("mnn_dm_", ndims, "_umap")) +
  ggplot2::scale_color_manual(values = sample_info$color,
                              breaks = sample_info$project_name) +
  Seurat::NoAxes() + ggplot2::ggtitle("RNA - mnn - DM - UMAP") +
  ggplot2::theme(aspect.ratio = 1,
                 plot.title = element_text(hjust = 0.5)) +
  ggplot2::guides(color = guide_legend(override.aes = list(size = 3), ncol = 1))
```

We visualize the annotation :

```{r see_dm_umap_celltype2, fig.width = 8, fig.height = 7}
Seurat::DimPlot(sobj, group.by = "cell_type",
                reduction = paste0("mnn_dm_", ndims, "_umap"),
                cols = color_markers) +
  Seurat::NoAxes() + ggplot2::ggtitle("RNA - mnn - DM - UMAP") +
  ggplot2::theme(aspect.ratio = 1,
                 plot.title = element_text(hjust = 0.5)) +
  ggplot2::guides(color = guide_legend(override.aes = list(size = 3), ncol = 1))
```

We make a representation split by origin :

```{r plot_split, fig.width = 12, fig.height = 17}
plot_list = aquarius::plot_split_dimred(sobj,
                                        reduction = paste0("mnn_dm_", ndims, "_umap"),
                                        split_by = "project_name",
                                        split_color = sample_info$color,
                                        group_by = "cell_type",
                                        group_color = color_markers)

patchwork::wrap_plots(plot_list, ncol = 4) +
  patchwork::plot_layout(guides = "collect") &
  guides(color = guide_legend(override.aes = list(size = 4), title = "Cell type"))
```


# Features

We represent expression level for genes of interest on the projection. We build a custom function to build a feature plot, and make a word cloud plot as top right corner inset :

```{r plot_feature, class.source = "fold-hide"}
name2D = paste0("mnn_dm_", ndims, "_umap")
  
plot_feature = function(gene) {
  ## Feature Plot
  p1 = Seurat::FeaturePlot(sobj, features = gene, reduction = name2D) +
    ggplot2::scale_color_gradientn(colors = aquarius::color_gene) +
    ggplot2::theme(aspect.ratio = 1) +
    Seurat::NoAxes()
  
  ## Word Cloud
  df = data.frame(project_name = levels(sobj$project_name),
                  row.names = levels(sobj$project_name))
  cells_associated_id = sobj@meta.data[Seurat::FetchData(sobj, gene)[, 1] > 0, "project_name"]
  df$number_cells_yes = table(cells_associated_id)[rownames(df)] %>% as.vector()
  df$number_cells_total = table(sobj$project_name)[rownames(df)] %>% as.vector()
  df$prop_cells = df$number_cells_yes/df$number_cells_total
  
  p2 = ggplot2::ggplot(df, aes(label = project_name, size = prop_cells, color = project_name)) +
    ggwordcloud::geom_text_wordcloud(seed = 123) +
    ggplot2::scale_color_manual(values = sample_info$color,
                                breaks = sample_info$project_name) +
    ggplot2::scale_size_area(max_size = 7) +
    ggplot2::theme_minimal()
  
  ## Patchwork
  p = p1 +
    patchwork::inset_element(p2,
                             left = 0.75, bottom = 0.75,
                             right = 1.17, top = 1.12)
  
  p = patchwork::wrap_plots(list(p1, p2), heights = c(5,1), ncol = 1)
  
  return(p)
}
```

```{r SOX9, fig.width = 12, fig.height = 85}
genes = c("SOX10", "SOX9", "MGP", "DCN",
          "ERBB3", "ERBB2", "PLP1", "KCNA1", "KCNA2",
          "CRABP1", "PDGFRA", "PDGFRB", "PDGFA", "PDGFB",
          "MIF", "TAGLN", "TAGLN2", "ACTA2",
          "ZEB1", "ZEB2", "ALDH1A1", "NES", "ENG", "DLK1")

plot_list = lapply(genes, FUN = plot_feature)

patchwork::wrap_plots(plot_list, ncol = 2)
```

# Save

We save the Seurat object :

```{r save_sobj}
saveRDS(sobj, file = paste0(out_dir, "/", save_name, "_sobj.rds"))
```


# R Session

```{r sessioninfo, echo = FALSE, fold_output = TRUE}
sessionInfo()
```

